---
title: "Acc_Show_Estimates_For_Full_Model"
author: "Jason McCarley & Megan Bartlett"
date: "19/August/2018"
output:
  html_document: default
  pdf_document: default
  word_document: default
---


```{r, echo = FALSE, warning=FALSE, message=FALSE}
library (tidyverse)
library (coda)
library(dplyr)

rm(list = ls())
# p = dirname(rstudioapi::getSourceEditorContext()$path)
# setwd(p)

load(here("analysis/Acc_Aid_x_Condition.Rdata"))

```
***
***
***
#### Means and 95% highest-density intervals of MCMC sample chains.

*** 
Max Rhat: `r max(samples$BUGSoutput$summary[,8])`   
DIC: `r samples$BUGSoutput$DIC`

```{r echo = FALSE, message = FALSE, warning=FALSE}
summarise <- function(my.samples, theta, diff = FALSE) {
  # my.samples should be BUGSoutput produced by jags
  # theta is a string that names the parameter that we want summarised
  theta.samples <- as.mcmc(my.samples$sims.matrix[,theta]) # get samples for the parameter we are interested in
  M = mean(theta.samples)
  lb = HPDinterval(theta.samples)[1] # lower bound of HDI
  ub = HPDinterval(theta.samples)[2] # upper bound

  # if these data are difference scores
  if (diff == TRUE)
  {
    p.neg = length(theta.samples[theta.samples < 0])/length(theta.samples) * 100 # percentage of posterior distribution < 0
    p.pos = length(theta.samples[theta.samples > 0])/length(theta.samples) * 100 # percentage > 0
    sprintf ('M = %.2f, HDI = [%.2f, %.2f], %.0f%% < 0 < %1.0f%%', M, lb, ub, p.neg, p.pos)
  } else
  {
    p.neg = length(theta.samples[theta.samples < 0])/length(theta.samples) * 100 # percentage of posterior distribution < 0
    p.pos = length(theta.samples[theta.samples > 0])/length(theta.samples) * 100 # percentage > 0
    sprintf ('M = %.2f, HDI = [%.2f, %.2f]', M, lb, ub)
  }
}


```


```{r echo = FALSE, message = FALSE, warning=FALSE}
p_data <- function(my.samples, theta) {
  # my.samples should be BUGSoutput produced by jags
  # theta is a string that names the parameter that we want summarised
  theta.samples <- as.mcmc(my.samples$sims.matrix[,theta]) # get samples for the parameter we are interested in
  M = mean(theta.samples)
  lb = HPDinterval(theta.samples)[1] # lower bound of HDI
  ub = HPDinterval(theta.samples)[2] # upper bound

  params = data.frame(M,lb,ub)
  return(params)
  
}


```


```{r Acc_cell_CI echo = FALSE, message = FALSE, warning=FALSE}

Model_Acc =data.frame(condition = c(rep("Static, By Event",2),rep("Dynamic, By Event",2),rep("Dynamic, Cumulative",2)),
                      aided = c("Unaided","Aided"),
                      Acc_M = rep(NA,6),
                      Acc_lb = rep(NA,6),
                      Acc_ub = rep(NA,6),
                      Opt_dif_M = rep(NA,6),
                      Opt_dif_lb = rep(NA,6),
                      Opt_dif_ub = rep(NA,6))
Model_Acc$condition = factor(Model_Acc$condition, levels = c("Static, By Event","Dynamic, By Event", "Dynamic, Cumulative"), ordered = TRUE)
Model_Acc$aided = factor(Model_Acc$aided, levels = c("Unaided","Aided"), ordered = TRUE)

 Model_Acc[1,3:5] = p_data(samples$BUGSoutput, 'd_m[1,1]')
 Model_Acc[2,3:5] = p_data(samples$BUGSoutput, 'd_m[1,2]')
 Model_Acc[3,3:5] = p_data(samples$BUGSoutput, 'd_m[2,1]')
 Model_Acc[4,3:5] = p_data(samples$BUGSoutput, 'd_m[2,2]')
 Model_Acc[5,3:5] = p_data(samples$BUGSoutput, 'd_m[3,1]')
 Model_Acc[6,3:5] = p_data(samples$BUGSoutput, 'd_m[3,2]')
 Model_Acc[1,6:8] = p_data(samples$BUGSoutput, 'c_m[1,1]')
 Model_Acc[2,6:8] = p_data(samples$BUGSoutput, 'c_m[1,2]')
 Model_Acc[3,6:8] = p_data(samples$BUGSoutput, 'c_m[2,1]')
 Model_Acc[4,6:8] = p_data(samples$BUGSoutput, 'c_m[2,2]')
 Model_Acc[5,6:8] = p_data(samples$BUGSoutput, 'c_m[3,1]')
 Model_Acc[6,6:8] = p_data(samples$BUGSoutput, 'c_m[3,2]')

 save(Model_Acc,file = here("analysis/Model_Acc_cell_CI.Rdata"))
 

```


```{r Acc_inf_CI echo = FALSE, message = FALSE, warning=FALSE}

# comparison = c("Aid_Static","Static.Current_Unaided","Static.Current_Aided","Aid_Current","Current.Cumulative_Unaided","CurrentCumulative_Aided")
Model_Acc =data.frame(condition = c("Aid_Static","Static.Current_Unaided","Static.Current_Aided",
                                    "Aid_Current","Current.Cumulative_Unaided","CurrentCumulative_Aided"),
                      Acc_M = rep(NA,6),
                      Acc_lb = rep(NA,6),
                      Acc_ub = rep(NA,6),
                      Opt_dif_M = rep(NA,6),
                      Opt_dif_lb = rep(NA,6),
                      Opt_dif_ub = rep(NA,6))
# Model_Acc$condition = factor(Model_Acc$condition, levels = c("Static, By Event","Dynamic, By Event", "Dynamic, Cumulative"), ordered = TRUE)
# Model_Acc$aided = factor(Model_Acc$aided, levels = c("Unaided","Aided"), ordered = TRUE)

 Model_Acc[1,2:4] = p_data(samples$BUGSoutput, 'd_aid.static')
 Model_Acc[2,2:4] = p_data(samples$BUGSoutput, 'd_display.static.current')
 Model_Acc[3,2:4] = p_data(samples$BUGSoutput, 'd_static.current.aided')
 Model_Acc[4,2:4] = p_data(samples$BUGSoutput, 'd_aid.current')
 Model_Acc[5,2:4] = p_data(samples$BUGSoutput, 'd_display.current.cumulative')
 Model_Acc[6,2:4] = p_data(samples$BUGSoutput, 'd_current.cumulative.aided')
 Model_Acc[1,5:7] = p_data(samples$BUGSoutput, 'c_aid.static')
 Model_Acc[2,5:7] = p_data(samples$BUGSoutput, 'c_display.static.current')
 Model_Acc[3,5:7] = p_data(samples$BUGSoutput, 'c_static.current.aided')
 Model_Acc[4,5:7] = p_data(samples$BUGSoutput, 'c_aid.current')
 Model_Acc[5,5:7] = p_data(samples$BUGSoutput, 'c_display.current.cumulative')
 Model_Acc[6,5:7] = p_data(samples$BUGSoutput, 'c_current.cumulative.aided')

 save(Model_Acc,file = here("analysis/Model_Acc_inf_CI.Rdata"))
 

```









```{r Acc_plot, eval = FALSE, echo = FALSE, message = FALSE, warning=FALSE, fig.width=12, fig.height=4.5}

rm(list = ls())
load(here("analysis/Model_Acc_Cell_CI.Rdata"))
load(here("analysis/Accuracy.Rdata"))
cmat_accuracy %<>% mutate(condition = recode(condition, Static = "Static, By Event",
                                    Current = "Dynamic, By Event",
                                    Cumulative = "Dynamic, Cumulative")) #,

pos_dodge = 0.5
Acc_CI <- ggplot(data = Model_Acc, mapping=aes(x = condition, y = Acc_M, fill = aided)) + 
  geom_dotplot(binaxis='y', stackdir='center', dotsize=3, binwidth = .01, position = position_dodge(pos_dodge)) +
  geom_errorbar(data = Model_Acc, mapping=aes(x = condition, ymin = Acc_lb, ymax = Acc_ub),
                width = .5, position = position_dodge(pos_dodge)) +
  labs(x = "Display Condition", y = "Accuracy", fill = "Aiding") +
  geom_violin(data = cmat_accuracy, mapping=aes(x = condition, y = resp_acc),alpha = .5, position = position_dodge(pos_dodge)) + 
  theme_classic() + scale_y_continuous(labels = percent, limits = c(0,1)) +
  # stat_summary(fun.y=mean, geom="point", shape=21, size=3, stroke = 1.25, aes (fill = aided),position = position_dodge(pos_dodge)) +
  scale_fill_manual(values=c("gold4", "gold1"))



Opt_dif_CI <- ggplot(data = Model_Acc, aes (x = condition, y = Opt_dif_M, fill = aided)) + 
  geom_dotplot(data = Model_Acc, binaxis='y', stackdir='center', dotsize=3, binwidth = .01, position = position_dodge(pos_dodge)) +
  geom_errorbar(data = Model_Acc, mapping=aes(x = condition, ymin = Opt_dif_lb, ymax = Opt_dif_ub),width = .5,
                position = position_dodge(pos_dodge)) +
  labs(x = "Display Condition", y = "Accuracy relative to Optimal", fill = "Aiding") +
  geom_violin(data = cmat_accuracy, mapping=aes(x = condition, y = norm_dif),alpha = .5, position = position_dodge(pos_dodge)) + 
  theme_classic() + scale_y_continuous(labels = percent, limits = c(-.5,.5)) +
  # stat_summary(fun.y=mean, geom="point", shape=21, size=3, stroke = 1.25, aes (fill = aided),position = position_dodge(pos_dodge)) +
  scale_fill_manual(values=c("darkorange4", "darkorange1"))


grid.arrange(Acc_CI,Opt_dif_CI,ncol=2)



```




***
***

Static Unaided Acc: `r summarise(samples$BUGSoutput, 'd_m[1,1]')`   
Static Aided Acc: `r summarise(samples$BUGSoutput, 'd_m[1,2]')`  
Static Automation Acc benefit: `r summarise(samples$BUGSoutput, 'd_aid.effect[1]')`  

Current Unaided Acc: `r summarise(samples$BUGSoutput, 'd_m[2,1]')`   
Current Aided Acc: `r summarise(samples$BUGSoutput, 'd_m[2,2]')`  
Current Automation Acc benefit: `r summarise(samples$BUGSoutput, 'd_aid.effect[2]')`  

Cumulative Unaided Acc: `r summarise(samples$BUGSoutput, 'd_m[3,1]')`   
Cumulative Aided Acc: `r summarise(samples$BUGSoutput, 'd_m[3,2]')`  
Cumulative Automation Acc benefit: `r summarise(samples$BUGSoutput, 'd_aid.effect[3]')`  

***
***

Static Unaided Opt Diff: `r summarise(samples$BUGSoutput, 'c_m[1,1]')`   
Static Aided Opt Diff: `r summarise(samples$BUGSoutput, 'c_m[1,2]')`  
Static Automation Opt Diff benefit: `r summarise(samples$BUGSoutput, 'c_aid.effect[1]')`  

Current Unaided Opt Diff: `r summarise(samples$BUGSoutput, 'c_m[2,1]')`   
Current Aided Opt Diff: `r summarise(samples$BUGSoutput, 'c_m[2,2]')`  
Current Automation Opt Diff benefit: `r summarise(samples$BUGSoutput, 'c_aid.effect[2]')`  

Cumulative Unaided Opt Diff: `r summarise(samples$BUGSoutput, 'c_m[3,1]')`   
Cumulative Aided Opt Diff: `r summarise(samples$BUGSoutput, 'c_m[3,2]')`  
Cumulative Automation Opt Diff benefit: `r summarise(samples$BUGSoutput, 'c_aid.effect[3]')`  


***

